Highlighting Disputed Information on the Web

### 2009-10-16 papers/www_disputefinder/disputefinder.tex
Updates to WWW paper. Added all claims API. Added ACM TechNews and CSM to Press list

% \newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
% \newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
% \newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
% \newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

\newcommand{\want}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\node}[1]{}

@@

\additionalauthors{Whoever else wants to help out with the paper. Let me know.}

@@

A great thing about the web is that it allows anyone to publish whatever they want without having to go through a higher authority that must approve everything that is written. However a consequence of this is that much of the information that one encounters on the web has not been certified by an authority that a user trusts, and so it becomes much harder for a user to decide whether they should trust the information they are reading.

\idea{Of course, old media wasn't entirely trustworthy either}

However the old way of doing things had certain advantages.

One frustrating consequence of this is that

 that much of the information on the web comes from sources that users do not know whether they can trust.

When the available media is filtered through a small number of publishers,

The web contains a huge amount of information, but some of this information is incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. 
If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
Even if a user tries to be careful, they can still be caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Dispute Finder, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
When a user clicks on a highlighted snippet, Dispute Finder presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

Dispute Finder relies on users to identify disputed claims, to find instances of these claims on web pages, and to vote for the sources that provide the best support or opposition for a claim. 
Dispute Finder is designed to cater to two primary usage scenarios:

\begin{description}
\item[Activists] care strongly about particular issues. They use Dispute Finder to mark snippets that make claims that they disagree with. They are motivated by a desire to make other readers see that these claims are disputed and learn about the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Dispute Finder as a browser extension so that it will highlight disputed claims and show them opposing points of view.
\end{description}

The same user may be an Activist for some issues and a Sceptical Reader for others.

\todo{Claim panel should have 'more' buttons}

Dispute Finder's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.

\todo{Talk about automatically including all arguments from Snopes}
\todo{I think we need to do some kind of evaluation of the new interface, even if it is just showing it to some people, or having people in the lab try it.}
\todo{Need figures saying how efficient it is for an activist user to mark up a topic}

% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
% 	\caption{Dispute Finder connects claims to each other and to web snippets}
% 	\label{summarygraph}
% 	\end{center}
% \end{figure}

\section{Related Work}
\todo{Don't cite things that aren't relevant}

Dispute Finder builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Dispute Finder interesting is the way that it applies ideas from these different domains to the task of helping users deal with misinformation and bias on the web.

\subsection{Checking Accuracy and Bias on the Web}

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Dispute Finder's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. The advantage of Dispute Finder is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.

%We use Fact Check as a useful source of disputed claims.

% FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Dispute Finder as they appear.

\todo{Make sure we stay in sync}

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic. Unlike Dispute Finder, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. Unlike these Wikipedia-based systems, Dispute Finder does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.

% 
% 
% NewsCube~\cite{Park2009}.
% Wikipedia fixes Vandalism~\cite{Viegas2004}.
% Trustworthiness~\cite{Gil2006}.
% WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
% Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
% SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.

>>>>

\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

%\newcommand{\want}[1]{}
%\newcommand{\todo}[1]{}
%\newcommand{\idea}[1]{}
%\newcommand{\node}[1]{}

@@

\additionalauthors{Additional authors: Tad Hirsch (Intel Research PaPR, email: {\texttt{tad.hirsch@intel.com}}) and Tye Rattenbury (Intel Research PaPR), email: {\texttt{tye.rattenbury@intel.com}})}

@@

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. 
If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.
Even if a user tries to be careful, they can still be caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we describe Dispute Finder, a service that informs a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in.

If a user has installed the Dispute Finder browser extension then it will highlight snippets of text on the web that make claims that Dispute Finder believes are disputed (Figure~\ref{highlight}). 
When a user clicks on a highlighted snippet, Dispute Finder will present a list of articles that present alternative points of view, each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).

Dispute Finder consists of a database, an API, and a firefox browser extension. The database contains information about the disputed claims that are known to be made on web sites, and hints about how to tell when a web page is making such a claim. The API allows an external client to determine whether particular content is making a disputed cliam. The firefox extension uses the API to determine whether the web pages a user browses make disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

@@

There are a number of design decisions that must be made when building a system such as this, which we will address in the remainder of the paper. In particular:

\begin{description}
\item[What claims are disputed?] In order to highlight claims as being disputed, we need to know what claims these are. To be useful, the set of known disputed claims needs to be both large (so people see some benefit) and accurate (so that people don't get annoyed by things that aren't actually disputed. We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. There are also other interesting alternative approaches that may be worth exploring.

\item[What disputed claims should we tell the user about?] In some sense almost everything is disputed by someone. If we highlighted everything that was disputed by anyone then the tool would be too noisy to be useful. The challenge is to determine when the other point of view is something the user might take seriously. We do not yet have a large enough database of disputed claims for this to be a serious problem, but we believe that there may be interesting solutions.

\item[How do we tell that a snippet is making a disputed claim?] If a user is reading a web page that might contain disputed claims, then how do we determine which sentences are making disputed claims? We have experimented with several different approaches, each of which has different advantages and disadvantages. One can ask users to mark snippets individually. One can build a search tool that allows a user to find and mark similar snippets in bulk. One can provide an interface that allows a user to train a machine learning classifier to recognize snippets. One can use a textual entailment algorithm to recognize phrases that seem to have a similar meaning to the claim.

\item[How do we add highlights to the pages a user browses?] If a user is reading web pages, how should we augment that experience with information about disputed claims? Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension~\cite{nolike-extension?}. Using a proxy~\cite{proxy?} has similar adoption problems to a browser extension, and is likely to break some web sites. Providing an API allows external sites such as news readers and search engines to provide information about disputed claims, but limits coverage to those sites that support the API. The best approach may be a combination.

\item[What information should we show someone about a disputed claim?] If someone clicked on a disputed claim on a web page, what information should we show them that will help them decide whether to talk the alternative points of view seriously. Alternatives include an argumentation graph, user comments, a wiki page, 
We experimented with providing an argumentation graph, user comments, aut
\end{description}

In order for Dispute Finder to be useful, it needs to provide a service that users will actually appreciate. It is thus important that we understand how users feel about disputed information. Dispute Finder is designed to cater to two personas. Each persona was created from interviews we conducted with people who we believe fit into these categories:

\todo{Use interviews to get some actual observations here. These are just fillers.}

\begin{description}

\item[Skeptical Readers] want to know when information they read is disputed. They are primarily motivated by a desire to avoid being misled. Although there are some sources that they strongly trust, they also regularly read web sites that they do not trust, and they are worried about being misled. In the abscence of Dispute Finder, they often try to verify information they read online by searching several web sites on the same topic, or checking something they have read on a known trusted site.

\item[Activists] care strongly about particular issues and are prepared to spend some time helping other users know that something they read is disputed. They are the same kinds of people who join protest groups, argue about topics online, post stories to news aggregators, or edit wikipedia. They are motivated by a desire to gain status by being publically seen to have led others to discover that important issues are disputed. They are also motivated by a desire to entertain themselves by seeing what disputed claims are being made and where online they are being made.

\end{description}

\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}

The same user may be an Activist for some issues and a Sceptical Reader for others. Dispute Finder is not useful for everyone. In our interviews, we encountered several people who either didn't rely on the internet as an important source of information, or only obtained important information from sources that they trust. If a user never reads information they care about from web sites that they don't entirely trust, then Dispute Finder will not be useful to them.

\todo{Should we explicitly list what we think are our key contributions?}

\section{Related Work}

Dispute Finder builds on prior work in several different areas. The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}. Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.

\todo{Add more references from the NewsCube paper}

\subsection{Fact Checking Sites}

If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com. If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org. These sites do an excellent job at presenting accurate and balanced information about controversial topics.

Dispute Finder is designed to deal with the cases where the user is not aware that the information they are reading is disputed and so does not realise that they should check it on one of these services, or does not know which of these services might have more information. Dispute Finder is designed to work together with fact checking sites like Snopes and Politifact. Indeed Dispute Finder automatically imports disputed claims made on Snopes or Politifact into its claim database, and will use articles from Snopes and Politifact as evidence about disputed claims.

\subsection{Analysing News}

News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader persective of the issue. Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the slant of the entire article. A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.

Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

\subsection{Highlighting Disputed Information}

Several previous tools have used highlighting to alert an author about information that they should perhaps be suspicious of. WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author.

Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, so that they can put forward their own point of view. Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips. There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}.

These annotation tools all allow a user to annotate a page with their thoughts on the same topic. In Dispute Finder, we do not allow a user to directly express their own opinions about a topic. Instead, the only way they can disagree with something that is said is to link it to an article from a trusted source that argues for a different point of view. We believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

Another key difference between these annotation tools and Dispute Finder is that these annotation tools all allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. By contrast, if a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that it appears.

\todo{Cite google quotation stuff and Ed Chi movable quotations stuff}

\subsection{Finding Repeated Information on the Web}

A key component of Dispute Finder is that in needs to identify phrases on the web that make a know disputed claim. The techniques that Dispute Finder uses have been influenced by related work that does similar things.

\cite{Kim2009} Efficient Overlap and Content Reuse Detection.

\cite{schillit?}

Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. Dispute Finder also creates new links between information, but it's links are created by users, rather than being mined automatically.

\cite{Something by Ed CHi about this}

\todo{Talk about textual entailment}

\todo{Talk about MemeTracker}

\subsection{Textual Entailment}

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in.
